The letter

### 2010-07-01 ltx/PLoS/SubmissionLetter.tex
small chage to submission letter
small edits to letter

This paper brings several new techniques to the field of computational biology, where as the title suggests, we have developed a data-driven framework for estimating the parameters of a neural field model. Our aim in this work is to model the intracortical connectivity and synaptic dynamics of an individual patient or experimental subject. These subject-specific neural field models will provide new avenues for the application of engineering techniques to neural systems, with application to epilepsy and other neurological disorders, and to brain-computer interfaces.

This paper is timely as it draws together and is built upon several cutting-edge technologies including:
\begin{itemize}
	\item increases in bandwidths in data acquisition systems, higher electrode technology and data storage capabilities that have led to significant advances in neurophysiological recording techniques, 
	\item developments in neural field theory that have led to valuable insights into the mass action of cortical systems,
	\item recent advances in computing power and nonlinear systems theory that have made possible state estimation from large-scale nonlinear spatio-temporal systems.
\end{itemize}

@@

The novel aspects of this paper include:
\begin{itemize}
	\item the representation of a continuum neural field model as a reduced finite-dimensional state-space model and the necessary conditions for representing the neural field by a basis function decomposition;
	\item derivations of the necessary conditions for placement and geometry of sensors/electrodes to sufficiently sample a neural field in order to capture the significant cortical dynamics;
	\item an implementation of the unscented Rauch-Tung-Striebel smoother for state estimation;
	\item a derivation of an algorithm for estimating intracortical connectivity and synaptic dynamics using the neural field equations.
\end{itemize}

>>>>

This paper brings several new techniques to the field of computational biology, where as the title suggests, we have developed a data-driven framework for estimating the parameters of a neural field model from electrophysiological data. Our aim in this work is to model the intracortical connectivity and synaptic dynamics of an individual patient or experimental subject. These subject-specific neural field models will provide new avenues for the application of engineering techniques to neural systems, particularly to epilepsy and other neurological disorders, and to brain-computer interfaces.

This paper is timely as it draws together and is built upon several cutting-edge technologies including:
\begin{itemize}
	\item increases in bandwidths in data acquisition systems, higher electrode technology and data storage capabilities that have led to significant advances in neurophysiological recording techniques, 
	\item developments in neural field theory that have led to valuable insights into the mass action of cortical systems,
	\item recent advances in computing power and nonlinear systems theory that have made possible state estimation from large-scale nonlinear spatiotemporal systems.
\end{itemize}

@@

The novel aspects of this paper include:
\begin{itemize}
	\item the representation of a continuum neural field model as a reduced finite-dimensional state-space model and the necessary conditions for representing the neural field by a basis function decomposition;
	\item derivations of the necessary conditions for placement and geometry of sensors/electrodes to sufficiently sample a neural field in order to capture the significant cortical dynamics;
	\item an implementation of the unscented Rauch-Tung-Striebel smoother for state estimation of a spatiotemporal neural system;
	\item a derivation of an algorithm for estimating intracortical connectivity and synaptic dynamics using the neural field equations.
\end{itemize}
